The effects of host galaxy properties on merging compact binaries detectable by LIGO

### 2016-09-13 paper/mnras/paper.tex
updates

%%% MNRAS stuff  %%%
%\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols

@@

We selected our simulated regions of interest from a volume of
uniform resolution, and resampled the region at very high
resolution using the volume renormalization technique \citep{Katz93}.
This technique allows us to follow the detailed physical processes
involved in galaxy evolution in our selected region while still
including large-scale torques from cosmic structure.  Our cosmological parameters are $\Omega_0 = 0.24$, $\Omega_{\rm baryon} = 0.04$, $\Lambda = 0.76$, h = 0.73, $\sigma_8 = 0.77$ 
 \citep{WMAP3} and we model the ionizing UV background
with the prescription from \citet{Haardt96}.  Our interstellar medium (ISM) model includes the non-equilibrium formation and destruction of H$_2$, which is incorporated in the cooling model along with metal lines, along with shielding of HI and H$_2$ \citep{Christensen12}.  Stars form
probabilistically from gas particles which meet density ($n_{min} =
0.1$ amu cm$^{-3}$) and temperature ($T_{max} = 10^3$ K) thresholds, though since star formation also depends on the H$_{\rm 2}$ content of a particle (see below) the densities are nearly always much higher than this threshold. If a gas
particle meets these criteria, it has a likelihood of forming a star
particle (representing a simple stellar population with a Kroupa IMF
\citep{Kroupa93}) which is given by

@@

We model supernova feedback using the
blastwave formalism described in \citet{McKee77} and implemented in
our simulations as in \citet{Stinson06}.  Each supernova releases
$E_{SN} = 10^{51}$ erg into the surrounding gas with a radius
determined by the blastwave equations.  These particles are not
allowed to cool for the duration of the blastwave, mimicking the
adiabatic expansion phase of a supernova explosion.  Previous works have found
that this set of parameters results in realistic galaxies which obey a
number of observed relations such as the mass-metallicity relation
\citep{Brooks07}, % JB: removed Kirby citation
 the Tully-Fisher relation \citep{Christensen16}, and
the size-luminosity relation \citep{Brooks11}, as well as reproduce
the detailed characteristics of bulgeless dwarf galaxies
\citep{Governato10,Governato12}, low-mass disk galaxies with bulges \citep{Christensen14b}, and the Milky Way \citep{Guedes11}.

Metals are created in supernova explosions
and deposited directly to the gas within the blast radius.  Stellar
masses are converted to ages as described by \citet{Raiteri96}, and
stars more massive than 8 M$_\odot$ are able to undergo a Type II
supernova.  We follow metal enrichment from both Type II and Type 1a
supernova, with metal yields derived from \citet{Weaver93} and
\citet{Thielemann86} respectively. {\bf Richard:
 We adopt a fiducial Salpeter IMF.   We do not
 self-consistently evolve our population of compact binaries and metallicity: for simplicity and consistent with common
 practice, our model for chemical evolution is derived from isolated stars.  
 As described in ZZZ [PROBABLY NEED A PLOT], the  derived cosmological metal evolution and star formation rate history derived using this
 procedure is broadly consistent with the cosmological star formation history and metallicity evolution of the universe.
 In particular, our procedure in bulk is broadly consistent with previous work on star formation over cosmic time,
 including  phenomenological models for cosmological
 metal evolution and star formation history overall  \cite{2016MNRAS.461.3877D}; the mass-metallicity relationship; and
 the mass-metallicity-SFR correlation
 \cite{2010MNRAS.408.2115M,2016MNRAS.tmp.1187H} NEED MORE REPRESENTATIVE CITATIONS BESIDES THE ONE THE REFEREE WANTS.  Our procedure also yields scatter in metallicity between galaxies,
 consistent with the observed dispersion in the mass-metallicity relation (ZZZ; Panter?) and observation of DLAs
 \cite{2015MNRAS.452L..36D}; see YYY for comparison.
}

>>>>

%%% MNRAS stuff  %%%
\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols

@@

We selected our simulated regions of interest from a volume of
uniform resolution, and resampled the region at very high
resolution using the volume renormalization technique \citep{Katz93}.
This technique allows us to follow the detailed physical processes
involved in galaxy evolution in our selected region while still
including large-scale torques from cosmic structure.  Our cosmological parameters are $\Omega_0 = 0.24$, $\Omega_{\rm baryon} = 0.04$, $\Lambda = 0.76$, h = 0.73, $\sigma_8 = 0.77$ 
 \citep{WMAP3}.  \footnote{Since we are simulating individual galaxy environments rather than large populations of halos, the selection of cosmological parameters provides a negligible contribution to the variance in the overall evolutionary history of galaxies in our simulations. } We model the ionizing UV background
with the prescription from \citet{Haardt96}.  Our interstellar medium (ISM) model includes the non-equilibrium formation and destruction of H$_2$, which is incorporated in the cooling model along with metal lines, along with shielding of HI and H$_2$ \citep{Christensen12}.  Stars form
probabilistically from gas particles which meet density ($n_{min} =
0.1$ amu cm$^{-3}$) and temperature ($T_{max} = 10^3$ K) thresholds, though since star formation also depends on the H$_{\rm 2}$ content of a particle (see below) the densities are nearly always much higher than this threshold. If a gas
particle meets these criteria, it has a likelihood of forming a star
particle (representing a simple stellar population with a Kroupa IMF
\citep{Kroupa93}) which is given by

@@

We model supernova feedback using the
blastwave formalism described in \citet{McKee77} and implemented in
our simulations as in \citet{Stinson06}.  Each supernova releases
$E_{SN} = 10^{51}$ erg into the surrounding gas with a radius
determined by the blastwave equations.  These particles are not
allowed to cool for the duration of the blastwave, mimicking the
adiabatic expansion phase of a supernova explosion.  Previous works have found
that this set of parameters results in realistic galaxies which obey a
number of observed relations such as the mass-metallicity relation
\citep{Brooks07,Christensen16}, % JB: removed Kirby citation
 the Tully-Fisher relation \citep{Christensen16}, and
the size-luminosity relation \citep{Brooks11}, as well as reproduce
the detailed characteristics of bulgeless dwarf galaxies
\citep{Governato10,Governato12}, low-mass disk galaxies with bulges \citep{Christensen14b}, and the Milky Way \citep{Guedes11}.

Metals are created in supernova explosions
and deposited directly to the gas within the blast radius.  Stellar
masses are converted to ages as described by \citet{Raiteri96}, and
stars more massive than 8 M$_\odot$ are able to undergo a Type II
supernova.  \jillianremark{  For Type II supernovae, iron and oxygen are produced according to the analytic fits used in \citet{Raiteri96} using the yields from \citet{Woosley95}:

\begin{equation}
M_{\rm Fe} = 2.802 \times 10^{-4} M_*^{1.864}
\end{equation}
\begin{equation}
M_{\rm O} = 4.586 \times 10^{-4} M_*^{2.721}.
\end{equation}

Feedback from Type Ia supernovae also follows \citet{Raiteri96}.  Each supernova produces $0.63\msun$ iron and $0.13 \msun$ oxygen \citet{Thielemann86}.  Metal production from stellar winds is also included; we implement stellar wind feedback based on \citet{Kennicutt94} and the returned mass fraction is derived using a function by \citet{Weidemann87}.  The returned gas has the same metallicity as the star particle.

We do not include specific prescriptions for metal distribution based on initial metallicity (such as for Population III stars) or variations in IMF.  }

%{\bf Richard:
% We adopt a fiducial Salpeter IMF.   We do not
% self-consistently evolve our population of compact binaries and metallicity: for simplicity and consistent with common
% practice, our model for chemical evolution is derived from isolated stars.  
% As described in ZZZ [PROBABLY NEED A PLOT], the  derived cosmological metal evolution and star formation rate history derived using this
% procedure is broadly consistent with the cosmological star formation history and metallicity evolution of the universe.
% In particular, our procedure in bulk is broadly consistent with previous work on star formation over cosmic time,
% including  phenomenological models for cosmological
% metal evolution and star formation history overall  \cite{2016MNRAS.461.3877D}; the mass-metallicity relationship; and
% the mass-metallicity-SFR correlation
% \cite{2010MNRAS.408.2115M,2016MNRAS.tmp.1187H} NEED MORE REPRESENTATIVE CITATIONS BESIDES THE ONE THE REFEREE WANTS.  Our procedure also yields scatter in metallicity between galaxies,
% consistent with the observed dispersion in the mass-metallicity relation (ZZZ; Panter?) and observation of DLAs
% \cite{2015MNRAS.452L..36D}; see YYY for comparison.
%}
